# Portland Metropolitan Area
## ITHIM-R Implementation (December, 2017)
```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
#options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
#library("ggplot2")
#library("devtools")
#library("reshape2")
#library("plyr")
#library("dplyr")
options(width = 110)
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```
For a comparison to the EXCEL workbook implementation of ITHIM we use
the `devel` branch of the _ITHIM_ repository maintained in the ITHIM
organization on Github.

```{r ITHIMBasline, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
library("devtools")
install_github("ITHIM/ITHIM", ref="excel")
library("ITHIM")
```

### Create an ITHIM object

Next we use three files to create an ITHIM R object.

```{r InputFiles, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
activeTransportFile <- system.file("activeTravelOHAS.csv", package = "ITHIM")
GBDFile <- system.file("portland-burden-sgy-reformatted.csv", package = "ITHIM")
FFile <- system.file("F.portland.11_21_2017.csv", package = "ITHIM")

ITHIM.baseline <- createITHIM( activeTransportFile = activeTransportFile, GBDFile = GBDFile, FFile = FFile)
```


```{r ExtraParams, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE, echo = FALSE}
muNonTravelMatrix <- readRDS(file = "~/younkin2017/data/muNonTravelMatrix.portland.rds")
(param.nonTravel <- readRDS(file = "~/younkin2017/data/parameters.LA.untransformed.ungrouped.rds"))
```

### Adjustment to Walk/Bike Relative Means

In the OHAS study we excluded the first two age classes and so we insert
these values found in the EXCEL workbook.  An adjustment is made to
ageClass 8 cycling values as well because the values in the data are
zero.

```{r adjustments, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
Rwt <- ITHIM.baseline@parameters@Rwt
Rwt[1,] <- c(0.4305,0.3471)
Rwt[2,] <- c(0.4934,0.4814)

Rct <- ITHIM.baseline@parameters@Rct
Rct[1,] <- c(0.2935,0.1231)
Rct[2,] <- c(1.3194,0.8278)
Rct[8,] <- c(0.1,0.1)
```

### Update to Baseline Object
Now we update the ITHIM object with the mean travel times provided by
Metro, along with: _cv_ (coefficient of variation of active transport
time) and _muNonTravel_ (overall mean leisure activity).

```{r ITHIMObjs, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.baseline <- update(ITHIM.baseline, list(
                                             muwt = 47.2061,
                                             Rwt = Rwt,
                                             muct = 15.0722,
                                             Rct = Rct,
                                             cv = 1.6483,
                                             quantiles = c(0.1,0.3,0.5,0.7,0.9),
                                             EXCEL = TRUE
                                             ))
```


### Scenarios
Now we construct four scenarios by updating the mean walk and cycle
times.

```{r Scenarios, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.2040.nobuild <-     update(ITHIM.baseline, list(muwt = 44.91, muct = 17.82, cv = 1.6475))
ITHIM.2027.constrained <- update(ITHIM.baseline, list(muwt = 46.21, muct = 17.04, cv = 1.6467))
ITHIM.2040.constrained <- update(ITHIM.baseline, list(muwt = 46.41, muct = 18.85, cv = 1.6437))
ITHIM.2040.strategic <-   update(ITHIM.baseline, list(muwt = 46.37, muct = 18.57, cv = 1.6442))

ITHIM.scenario.list <- list(
    ITHIM.2027.constrained = ITHIM.2027.constrained,
    ITHIM.2040.nobuild = ITHIM.2040.nobuild,
    ITHIM.2040.constrained = ITHIM.2040.constrained,
    ITHIM.2040.strategic = ITHIM.2040.strategic
)
```
### Percent Disease Burden Reduction

To tabulate the percent change in disease burden across all scenarios
we use the function _superTabulate_ and output the results to _results.csv_

```{r results, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE, tidy.opts=list(width.cutoff=250)}
results.df <- superTabulate(ITHIM.baseline, ITHIM.scenario.list)
write.csv(results.df, file = "./results.csv", quote = FALSE, row.names = FALSE)
head(results.df)
```

#### Session Info
```{r sessionInfo, message = TRUE, eval = TRUE, warning = TRUE, error = TRUE, echo = TRUE, tidy.opts=list(width.cutoff=100)}
sessionInfo()
```

```{r test, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE, echo = FALSE}
#muwt <- 44.91
AF <- c()
deltaB <- c()
muwtVec <- seq(1,120,length.out = 50)
for( muwt in muwtVec){
    for( muct in 1/3*muwtVec){
        ITHIM.test <- update(ITHIM.baseline, list(muwt = muwt, muct = muct, cv = 1.6475, EXCEL = TRUE))
        AF <- c(AF,getAF(ITHIM.baseline, ITHIM.test)$BreastCancer)
        deltaB <- c(deltaB, deltaBurden(ITHIM.baseline, ITHIM.test, bur = "daly", dis = "all"))
    }
}
```
