# Portland Metropolitan Area
## ITHIM-R Implementation (December, 2017)
```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
#options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
#library("ggplot2")
#library("devtools")
#library("reshape2")
#library("plyr")
#library("dplyr")
options(width = 110)
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```
For a comparison to the EXCEL workbook implementation of ITHIM we use
the `devel` branch of the _ITHIM_ repository maintained in the ITHIM
organization on Github.

```{r ITHIMBasline, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
library("devtools")
install_github("ITHIM/ITHIM", ref="devel")
library("ITHIM")
```

### Create an ITHIM object

Next we use three files to create an ITHIM R object.

```{r InputFiles, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
activeTransportFile <- system.file("activeTravelOHAS.csv", package = "ITHIM")
GBDFile <- system.file("gbd_Manuscript_2011-2015.csv", package = "ITHIM")
FFile <- system.file("F.portland.11_21_2017.csv", package = "ITHIM")

ITHIM.baseline <- createITHIM( activeTransportFile = activeTransportFile, GBDFile = GBDFile, FFile = FFile)
```
We also nee parameters that describe the leisure activity of the
population.  We load to R binaries created for _Younkin et al._
(2017).

```{r ExtraParams, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
muNonTravelMatrix <- readRDS(file = "~/younkin2017/data/muNonTravelMatrix.portland.rds")
(param.nonTravel <- readRDS(file = "~/younkin2017/data/parameters.LA.untransformed.ungrouped.rds"))
```

### Adjustment to Walk/Bike Relative Means

In the OHAS study we excluded the first two age classes and so we insert
these values found in the EXCEL workbook.  An adjustment is made to
ageClass 8 cycling values as well because the values in the data are
zero.

```{r adjustments, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
Rwt <- ITHIM.baseline@parameters@Rwt
Rwt[1,] <- c(0.43,0.35)
Rwt[2,] <- c(0.49,0.48)

Rct <- ITHIM.baseline@parameters@Rct
Rct[1,] <- c(0.29,0.12)
Rct[2,] <- c(1.32,0.83)
Rct[8,] <- c(0.1,0.1)
```

### Adjustment to Leisure Activity Relative Means


### Update to Baseline Object
Now we update the ITHIM object with the mean travel times provided by
Metro, along with: _cv_ (coefficient of variation of active transport
time) and _muNonTravel_ (overall mean leisure activity).

```{r ITHIMObjs, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.baseline <- update(ITHIM.baseline, list(
                                             muwt = 47.21,
                                             Rwt = Rwt,
                                             muct = 15.07,
                                             Rct = Rct,
                                             cv = 1.65,
                                             muNonTravel = param.nonTravel$meanMETs,
                                             muNonTravelMatrix = muNonTravelMatrix,
                                             cvNonTravel = param.nonTravel$sdMETs/param.nonTravel$meanMETs,
                                             quantiles = c(0.1,0.3,0.5,0.7,0.9)
                                             ))
```
### Scenarios
Now we construct four scenarios by updating the mean walk and cycle
times.

```{r Scenarios, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.2027.constrained <- update(ITHIM.baseline, list(muwt = 44.91, muct = 17.82))
ITHIM.2040.nobuild <-     update(ITHIM.baseline, list(muwt = 46.21, muct = 17.04))
ITHIM.2040.constrained <- update(ITHIM.baseline, list(muwt = 46.41, muct = 18.85))
ITHIM.2040.strategic <-   update(ITHIM.baseline, list(muwt = 46.37, muct = 18.57))

ITHIM.scenario.list <- list(
    ITHIM.2027.constrained = ITHIM.2027.constrained,
    ITHIM.2040.nobuild = ITHIM.2040.nobuild,
    ITHIM.2040.constrained = ITHIM.2040.constrained,
    ITHIM.2040.strategic = ITHIM.2040.strategic
)
```
### Percent Disease Burden Reduction

To tabulate the percent change in disease burden across all scenarios
we use the function _tabulateResults_ and output the results to _results.csv_

```{r results, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE, tidy.opts=list(width.cutoff=250)}
results.df <- tabulateResults(ITHIM.baseline, ITHIM.scenario.list)
write.csv(results.df, file = "~/Portland/results.csv", quote = FALSE, row.names = FALSE)
head(results.df)
```

### Leisure Activity Means

The values in the workbook for leisure activy are relatively high.
The values range from 44-65 MET-hrs./week which corresponds to 11-16
hrs./week of moderate physical activity for leisure.

Our analyis of the ATUS data yielded an overall mean of around 9
MET-hrs./week, or just over 2 hrs./week of moderate activity.

Let's set nonTravel activity to zero for comparison with the workbook.

```{r updateLA, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE, tidy.opts=list(width.cutoff=250)}
muNonTravel <- 0
ITHIM.baseline <- update(ITHIM.baseline, list(muNonTravel = muNonTravel))
ITHIM.2027.constrained <- update(ITHIM.2027.constrained, list(muNonTravel = muNonTravel))
ITHIM.2040.nobuild <- update(ITHIM.2040.nobuild, list(muNonTravel = muNonTravel))
ITHIM.2040.constrained <- update(ITHIM.2040.constrained, list(muNonTravel = muNonTravel))
ITHIM.2040.strategic <- update(ITHIM.2040.strategic, list(muNonTravel = muNonTravel))

ITHIM.scenario.list <- list(
    ITHIM.2027.constrained = ITHIM.2027.constrained,
    ITHIM.2040.nobuild = ITHIM.2040.nobuild,
    ITHIM.2040.constrained = ITHIM.2040.constrained,
    ITHIM.2040.strategic = ITHIM.2040.strategic
)
results.df <- tabulateResults(ITHIM.baseline, ITHIM.scenario.list)
ITHIM:::getAF(ITHIM.baseline, ITHIM.2027.constrained)$Dementia
```

Sources of discrepancies include:  different Rwt and Rct, different
MET value for walk, ceiling function use in EXCEL workbook.

#### Session Info
```{r sessionInfo, message = TRUE, eval = TRUE, warning = TRUE, error = TRUE, echo = TRUE, tidy.opts=list(width.cutoff=100)}
sessionInfo()
```
